A framework for mentored data science research

### 2019-12-18 Rmd/discussion.Rmd
updated anonymous version

One shortcoming of our initial framework was the relative lack of emphasis 
on best practices for 
computational reproducibility. This is one area that we would like to 
rectify in 
future mentoring activities. The 
University of Wisconsin-Madison has periodically offered a semester course 
in best practices for 
computationally reproducible research (https://kbroman.org/Tools4RR/). We 
especially see collaborative 
version control systems, such as Git and 
Github, as essential tools for the modern data scientist.

1. assessment of data science skills

1. assessment of attitudes (pre and post survey??)

@@

Our framework would benefit students more if we explicitly incorporate more 
mentoring activities. Through professional development courses at the University
of Wisconsin-Madison's Delta Program, we received training in how to offer 
professional support to students. While we both informally supported our
students, the Delta Program suggested
ways to encourage the student's professional development through structured
conversations and goal-setting. Additions like this would only enhance our 
framework.

>>>>

One shortcoming of our initial framework was the relative lack of emphasis 
on best practices for 
computational reproducibility. This is one area that we would like to 
rectify in 
future mentoring activities. The university has periodically offered a semester course 
in best practices for 
computationally reproducible research. We 
especially see collaborative 
version control systems, such as Git and 
Github, as essential tools for the modern data scientist.

@@

Our framework would benefit students more if we explicitly incorporate more 
mentoring activities. Through professional development courses at the university, we received training in how to offer 
professional support to students. While we both informally supported our
students, the professional development program suggested
ways to encourage the student's professional development through structured
conversations and goal-setting. Additions like this would only enhance our 
framework.

### 2019-12-18 Rmd/introduction.Rmd
added submission materials.
updated anonymous version

During the time when we first implemented our framework, we served as early-career instructors in 
the statistics department at the University of Wisconsin-Madison. One of us (Hanlon) had prior 
experience in mentoring students, while the other (Boehm) had none. Our initial 
conceptualization of mentoring drew heavily on ideas we first encountered in professional 
development 
activities, including the Delta Program's mentoring class (https://delta.wisc.edu) and @handelsman2005entering. 
Professor Erik Nordheim's class, "Teaching Statistics", 
influenced our approach to and philosophy of teaching statistics. 
We studied with Professor Nordheim early in our teaching 
careers, and his course's emphasis on backward design and active learning continues to influence our teaching practices (https://delta.wisc.edu).

>>>>

During the time when we first implemented our framework, we served as early-career instructors in 
the statistics department at a large university. One of us had prior 
experience in mentoring students, while the other had none. Our initial 
conceptualization of mentoring drew heavily on ideas we first encountered in professional 
development 
activities, including a professional development class and @handelsman2005entering. 
A professional development class, "Teaching Statistics", 
influenced our approach to and philosophy of teaching statistics. 
This course's emphasis on backward design and active learning continues to influence our teaching practices.
